\tool

### 2018-02-21 paper/paper.tex
Paper notes for future changes
Updated abstract and rewording contributions

\maketitle
\begin{abstract}
Software developers have access to numerous tools designed to increase productivity by automatically performing development tasks, but these tools are often ignored or undiscovered by programmers. This lack of tool awareness can have dangerous consequences, especially in the software engineering industry. Automated recommendation systems were created to improve tool discovery, however these systems are not as effective as user-to-user recommendations. To increase awareness of helpful development tools, we introduce \textit{\tool}, a novel system that integrates concepts of peer interactions and software engineering practices to increase tool discovery by effectively making recommendations to developers on open source GitHub projects.
\end{abstract}

@@

\begin{itemize}
 \item a novel system for researchers to recommend software engineering tools on GitHub, and
 \item an evaluation on the effectiveness of \tool~with \textsc{Error Prone}
 \end{itemize}

\section{Related Work}

Our implementation of \tool~builds on previous research examining tool discovery, lack of tool adoption among software engineers, and automated recommendation systems.

@@

%\pseudosubsection{Fix Localizaton}
%
%When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version. To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees. We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable. If the closest action is not a delete, then our approach take the location takes the location of that action. Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent. Additionally, the line of the fix had to be converted to the equivalent position in the pull request diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.

>>>>

\maketitle
\begin{abstract}
Toolsmiths have created many tools designed to increase worker productivity by automatically performing tasks, but these tools are often ignored or undiscovered. This lack of tool awareness can have significant consequences, especially in the software engineering industry. Automated recommendation systems were developed to help improve tool discovery, however these systems are less effective than user-to-user recommendations. To increase awareness of helpful development tools, we introduce \textit{\tool}, a new automated recommender system that integrates concepts from peer interactions and software engineering practices for researchers to increase discovery of their tools, and present an evaluation of how our system effectively recommends an open source static analysis tool to Java developers on GitHub projects.
\end{abstract}

@@

\begin{itemize}
 \item a novel recommender system for researchers to increase awareness of their software engineering tools, and
 \item an evaluation of \tool~ recommending \textsc{Error Prone} to GitHub developers
 \end{itemize}

\section{Related Work}
%TODO: Use related work from FSE committee
Our implementation of \tool~builds on previous research examining tool discovery, lack of tool adoption among software engineers, and automated recommendation systems.

@@

%\pseudosubsection{Fix Localizaton}
%TODO: Delete?
%When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version. To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees. We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable. If the closest action is not a delete, then our approach take the location takes the location of that action. Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent. Additionally, the line of the fix had to be converted to the equivalent position in the pull request diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.
